Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-17 Background.tex
Progress!

@@

While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence patches to normative models. The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour, with distortions to the perception of probability, and the value of outcomes. \citet{Tversky1992} subsequently addressed key issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics. The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is perceived as more of a loss than winning a shirt is a gain).

Under this model, the expected utility of any gamble is a function
of the probability of the outcomes, their utility to the gambler,
and the gambler's risk aversion. Essentially this is an extension
of the expected value criterion, which assumes that the expected value
is based only on the probability and objective value of outcomes.
By contrast, the utility framing is a subjective measure, allowing
differing preferences between gamblers. \citet{Neumann1953} later
formalised the theory, defining rational decision as acting to maximise
expected utility, where an individual's preferences are shown to fulfil
four axioms, namely completeness, transitivity, independence, and
continuity. Completeness requires that for any two lotteries A and
B, the decision maker prefers one to the other, or is indifferent.
Transitivity requires that if A is preferred to B, and B is preferred
to C, then A is also preferred to C. Continuity states that given
a scenario as in the transitivity axiom, there is some combination
of lotteries A and C where the decision maker is indifferent between
that combined lottery and B. Finally, independence maintains that
if one were to prefer gamble A to B, that preference holds if both
are combined with lottery C.

@@

A significant weakness of \ac{CPT} as a general theory of decision
making is that it fails to account for behaviour under intertemporal
choice, or rather does not attempt to address it. Generally, intertemporal
choice is assumed to be underpinned by the \ac{DU} model of \citet{Samuelson1937},
which proposes that the value of a thing right now is greater than
the value of it at some point in the future (jam today has more utility
than jam tomorrow), following an exponential relationship. A more
nuanced view of this has been proposed by \citet{Ainslie1991}, suggesting
that the relationship is hyperbolic rather than exponential. Both
models however fail to explain several inconsistencies, for example
\citet{Thaler1981} found that discounting rates were different between
gains and losses. \citet{Loewenstein1992} report a number of additional
inconsistencies that are not adequately resolved by \ac{DU} models,
and propose an alternative along the lines of \ac{CPT} to resolve
them while retaining the capabilities of Kahneman and Tversky's model
in immediate term choices.

>>>>

An alternative normative model of decision making is Bayesian decision theory, proposed by \citet{Robbins1964}, which is essentially the application of Bayesian style probabilities to the expected utility model. This allows probabilities used in reasoning to be subjective, which may allow for a better account of decisions from experience (see \citet{Hau2008,Hertwig2004} for results elucidating the distinction, and comparing the performance of several non-Bayesian models). This model has seen notable successes in practical problems \citep{McNamara1980,Survey2003,Kristensen1997}, but suggestions by several authors  that it could constitute an effective (top-down) model of learning \citep{Tenenbaum2006,Griffiths2010}, or induction \citep{Gallistel2012} in the brain have attracted substantil criticism, e.g. \citet{Bowers2012}, and \citet{Miller2012} responding to \citeauthor{Tenenbaum2006,Griffiths2010}, and \citeauthor{Gallistel2012} respectively.

@@

While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence patches to normative models. The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour \citep{Tversky1974}, with distortions to the perception of probability, and the value of outcomes \citep{Kahneman1984,Tversky1986} . \citet{Tversky1992} subsequently addressed issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics. The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is perceived as more of a loss than winning a shirt is a gain).
This last, known as the framing effect is particularly significant, see for example work by \citet{Toll2007} examining the relationship between loss and gain framings and success rates in giving up smoking, and \ac{NICE} guidance on framing of treatment options \citep{NICE2007}.

\ac{CPT} has been successful in explaining a number of anomalous results in decision tasks (see \citet{Camerer2004a} for a review), and \citet{Thaler2000} comments to the effect that the theory is promising, albeit incomplete, lacking for example any explanation of how frames are constructed. While an effective account of decision behaviour under risk, the theory does not attempt to resolve apparent inconsistencies that arise when outcomes are delayed, i.e. in situations of intertemporal choice. Historically, \ac{DU} \citep{Samuelson1937}, which effectively claims that the value of a thing now is exponentially greater than the promise of the same thing at some future date, has been applied to explain this. More recently, \citet{Ainslie1991} has suggested that discounting of future outcomes is hyperbolic, rather than exponential, although neither model is complete - both fail to account for results from \citet{Thaler1981} showing differing temporal discounting rates for losses and gains. \citet{Loewenstein1992} report additional failings in classic \ac{DU} models, and propose a modified form of \ac{CPT} which they suggest is able to handle both immediate, and intertemporal choice.

\begin{comment}Under this model, the expected utility of any gamble is a function
of the probability of the outcomes, their utility to the gambler,
and the gambler's risk aversion. Essentially this is an extension
of the expected value criterion, which assumes that the expected value
is based only on the probability and objective value of outcomes.
By contrast, the utility framing is a subjective measure, allowing
differing preferences between gamblers. \citet{Neumann1953} later
formalised the theory, defining rational decision as acting to maximise
expected utility, where an individual's preferences are shown to fulfil
four axioms, namely completeness, transitivity, independence, and
continuity. Completeness requires that for any two lotteries A and
B, the decision maker prefers one to the other, or is indifferent.
Transitivity requires that if A is preferred to B, and B is preferred
to C, then A is also preferred to C. Continuity states that given
a scenario as in the transitivity axiom, there is some combination
of lotteries A and C where the decision maker is indifferent between
that combined lottery and B. Finally, independence maintains that
if one were to prefer gamble A to B, that preference holds if both
are combined with lottery C.

@@

A significant weakness of \ac{CPT} as a general theory of decision
making is that it fails to account for behaviour under intertemporal
choice, or rather does not attempt to address it. Generally, intertemporal
choice is assumed to be underpinned by the \ac{DU} model of \citet{Samuelson1937},
which proposes that the value of a thing right now is greater than
the value of it at some point in the future (jam today has more utility
than jam tomorrow), following an exponential relationship. A more
nuanced view of this has been proposed by \citet{Ainslie1991}, suggesting
that the relationship is hyperbolic rather than exponential. Both
models however fail to explain several inconsistencies, for example
\citet{Thaler1981} found that discounting rates were different between
gains and losses. \citet{Loewenstein1992} report a number of additional
inconsistencies that are not adequately resolved by \ac{DU} models,
and propose an alternative along the lines of \ac{CPT} to resolve
them while retaining the capabilities of Kahneman and Tversky's model
in immediate term choices.
\end{comment}

### 2014-07-17 Introduction.tex
Progress!

In this paper we extend previous work by \cite{GrayDissert}.

The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly REFS. As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the method. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

@@

The remainder of this paper proceeds to provide a brief review of the methodological context (\ref{sub:games_signals}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).

>>>>

The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly REFS. As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the method. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we extend previous work by \cite{GrayDissert} drawing on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

@@

The remainder of this paper proceeds to provide a brief review of the methodological context (\ref{sec:lit_review}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).

### 2014-07-17 Methods.tex
Working on introduction
Progress!

\begin{table}
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(n_{w}\) & Number of women & 1000 \\ \hline
\(n_{m}\) & Number of midwives & 100 \\ \hline
\(r_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(q_{w}\) & Probability of women sharing & 0. \\ \hline
\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic

>>>>

\begin{table}
\center
\begin{tabular} {|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(n_{w}\) & Number of women & 1000 \\ \hline
\(n_{m}\) & Number of midwives & 100 \\ \hline
\(r_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
Runs & Simulation runs & 1000 \\ \hline
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(q_{w}\) & Probability of women sharing & 0. \\ \hline
\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}

\subsection{Information Sharing}

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing (section \ref{sub:info_sharing}) on the robustness of these trends. Table \ref{tab:sharing_params} gives the parameters explored, with a more complete exploration of the effects on the system as a whole performed as part of the global sensitivity analysis.

\begin{table}
\center
\begin{tabular} {|l | l | l| l| l|}
\hline
Name & Description & Min & Max & Step Size \\ \hline
\(q_{w}\) & Probability of women sharing & 0 & 1 & 0.25 \\ \hline
\(w_{w}\) & Weight of shared information for women & 0 & 1 & 0.25 \\ \hline
\(q_{m}\) & Probability of midwives sharing & 0 & 1 & 0.25 \\ \hline
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 & 0.25 \\ \hline
\end{tabular}
\caption[Table caption text]{Information sharing parameter ranges. \label{tab:sharing_params}}
\end{table}

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic \acp{ABMs}, although see \citet{Thiele2014} for a review of alternative techniques.

### 2014-07-17 Results.tex
Added tex  root for easier building
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.
Filler
Filler text to be rewritten
Working on introduction
Progress!

%!TEX root = disclosure_game.tex
\section{Discussion and Conclusions}
\label{sec:conclusion}

>>>>

%!TEX root = disclosure_game.tex
%Include the descent into chaos bit
\section{Results}
\label{sec:results}

LOOK AT MAH GRAFS!

\subsection{Qualitative Trends}
\label{sub:qt_results}

As shown in figure \ref{fig:qt_honesty}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results (figure \ref{fig:qt_ref}), which show that the majority of drinkers are referred, despite substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased.

\begin{figure}[h!]
\caption{Average fraction of population signalling honestly over appointments, across 100 runs.}
\label{fig:qt_honesty}
\end{figure}

\begin{figure}[h!]
\caption{Average fraction of population referred over appointments, across 100 runs.}
\label{fig:qt_ref}
\end{figure}

\subsection{Information Sharing}
\label{sub:sharing_results}

\subsection{Sensitivity Analysis}
\label{sub:sa_results}

The full results for the sensitivity analysis covering all twelve emulators are available in appendix \ref{}, and in this section we present selected results highlighting......
